Software

### 2025-11-28 software.qmd
add packages

>>>>

## `BASS`
I'm a developer of the `BASS` MATLAB Package ([Github](https://github.com/sandialabs/bass_matlab))

Implementation of Bayesian Adaptive Spline Surfaces in MATLAB. This is a MATLAB translation of the python library [pyBASS](https://github.com/lanl/pyBASS)

## `BayesPPR`
I'm a developer of the `BayesPPR` MATLAB Package ([Github](https://github.com/sandialabs/bayesppr_matlab))

A MATLAB implementation of Bayesian Projection Pursuit Regression (BayesPPR). This is a MATLAB translation of the python library [pyBayesPPR](https://github.com/gqcollins/pyBayesPPR)
